Palaeodistribution of crop progenitors and wild foods in the Southern Levant

### 2023-08-04 analysis/analysis.Rmd
Predict all climatologies

taxa <- c("Hordeum spontaneum" = "Hordeum spontaneum")
          # "Bolboshoenus spp." = "Bolboschoenus")

@@

# Model
# TODO: tune?
rand_forest(mode = "classification", trees = 1000) |>
  set_engine(
    "ranger",
    probability = TRUE,
    sample.fraction = c(2250 / n_background, 1), # TODO: parameterise
  ) -> 
  rf_model

@@

```{r predict}
# TODO: predict on all periods (maybe combine stars and collapse into dimension first?)
rf_pred_cur <- predict(climate$cur, rf_fit)
rf_pred_eh <- predict(climate$EH, rf_fit)
```

>>>>

# taxa <- c("Hordeum spontaneum" = "Hordeum spontaneum")
taxa <- c("Bolboshoenus spp." = "Bolboschoenus")

@@

# Model
# TODO: tune?
rand_forest(mode = "classification", trees = 1000) |>
  set_engine(
    "ranger",
    # probability = TRUE,
    sample.fraction = c(220 / n_background, 1), # TODO: parameterise
  ) -> 
  rf_model

@@

```{r predict}
# TODO: predict on all periods (maybe combine stars and collapse into dimension first?)
rf_pred_cur <- predict(climate$cur, rf_fit, type = "prob")
rf_pred_eh <- predict(climate$EH, rf_fit, type = "prob")
rf_pred_yds <- predict(climate$YDS, rf_fit, type = "prob")
rf_pred_ba <- predict(climate$BA, rf_fit, type = "prob")
rf_pred_hs1 <- predict(climate$HS1, rf_fit, type = "prob")
rf_pred_lgm <- predict(climate$LGM, rf_fit, type = "prob")

rf_pred <- c(rf_pred_cur, rf_pred_eh, rf_pred_yds, rf_pred_ba, rf_pred_hs1,
             rf_pred_lgm)
names(rf_pred) <- c("cur", "EH", "YDS", "BA", "HS1", "LGM")

ggplot() + 
  geom_stars(data = st_redimension(st_crop(rf_pred, w_asia))) + 
  facet_wrap(~new_dim)
```
